### 2022-06-16 paper/main.tex
added to analysis

\begin{table}[h!]
    \small
    \caption{General formatting requirements for thesis or dissertation}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \begin{tabular}{| m{1.25in} | m{3in} | m{0.75in} |}
    \hline
    \multicolumn{2}{|c|}{Formatting Requirement} & Fulfilled? \\ \hline
    Page margins & \begin{tabular}{ll}
        \begin{tabular}{c|c}
        Left & 1.5" \\ \hline
        Right & 1" \\ \hline
        Top & 1" \\ \hline
        Bottom & 1" \\ 
        \end{tabular} 
         &
        \begin{tabular}{c}
             {\scriptsize The 1.5” left margin } \\ 
             {\scriptsize leaves room for the } \\
             {\scriptsize manuscript to be bound.} 
        \end{tabular}
    \end{tabular} & \ \\ \hline
    Body text of manuscript & Double-spaced. Justifying the text at the right margin is optional & \  \\ \hline
    Font size & No smaller than 10-point and no larger than 14-point & \  \\ \hline
    Text color & All text should be black (including URLs) & \  \\ \hline
    New chapter & Each chapter begins at the top of a new page, with a 2” top margin & \  \\ \hline
    Prefatory headings, chapter names and section headings & All prefatory headings, chapter names and section headings should be formatted consistently & \  \\ \hline
    Footnotes or endnotes & Single-spaced, with a double space between each note & \  \\ \hline
    Bibliographic entries / works cited / references & Single-spaced, with an extra space between entries. Style and format should otherwise follow the style guide used for the rest of the thesis/dissertation & \  \\ \hline
    Long quotations & May be indented and single-spaced, though some style guides prefer them to be indented and double-spaced & \  \\ \hline
    Tables and figures & Must conform to the same margins as the text. If the table or figure is placed in landscape orientation (horizontally on page), the margins and page-number location must retain a portrait (vertical) orientation, as on a regular page. Tables and figures may be in color & \  \\ \hline
    Table and figure captions & Single-spaced. Should be in the same type as the body of the text & \  \\ \hline
    Hand lettering & Not permitted. Symbols, accent marks, and equations must be typescript & \  \\ \hline
    Corrections in pen or pencil & Not permitted. & \  \\ \hline
    Printed manuscript & Single-sided (simplex). Do not staple. Do not hole-punch. The manuscript should be clearly readable throughout, for both electronic and printed documents. Any photocopies should be checked to make sure they are legible. If there are questions regarding print quality, you are encouraged to consult The Graduate School & \  \\ \hline
	\end{tabular}
	\label{table:table-1}
\end{table}

@@

@@

\par A third variable that is considered is the documented violent crime rate of each MSA. This data is derived from the FBI's Uniform Crime Reporting statistics (REF / Footnote) \footnote{Data from the FBI mostly comes from the year that is most recent, 2019. However, not all municipalities report information, so there are slight estimations in the data (REF). Additionally, not all MSAs have documented 2019 data, so 2018 or 2017 data are used instead. The year gathered is documented in Appendix (REF)}. These values range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL). Documented crime data is also normalized using min-max normalization so that it can be compared to a similarly normalized crime discussion value from the Reddit data. Appendix (REF) contains the documented crime rate of all MSAs.

@@

\section{Results}
\par TODO: show graphs, maps, tables, etc. Discuss results in subsections

@@

>>>>

@@

(FIG)

@@

\par A third variable that is considered is the documented violent crime rate of each MSA. This data is derived from the FBI's Uniform Crime Reporting statistics (REF) \footnote{Data from the FBI mostly comes from the year that is most recent, 2019. However, not all municipalities report information, so there are slight estimations in the data (REF). Additionally, not all MSAs have documented 2019 data, so 2018 or 2017 data are used instead. The year gathered is documented in Appendix (REF)}. These values range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL). Documented crime data is also normalized using min-max normalization so that it can be compared to a similarly normalized crime discussion value from the Reddit data. Appendix (REF) contains the documented crime rate of all MSAs.

@@

(FIG)

\section{Results}

\subsection{Activity}

\par In total, the Reddit scraper gathered 161,166 posts between 384 subreddits. Posts were collected between April 5th, 2022 to May 31, 2022. Table \ref{table:table-1} details the ten most active subreddits of those monitored. Similarly, Table \ref{table:table-2} lists the ten most active subreddits when normalized by population.

\begin{table}[h!]
    \centering
    \small
    \caption{Most active Metropolitan Areas}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \begin{tabular}{| c | c | c |}
    \hline
    Metropolitan Statistical Area & Number of Posts & Population\\ \hline
    Austin-Round Rock-Georgetown, TX & 4,084 & 2,283,371 \\ \hline
    San Diego-Chula Vista-Carlsbad, CA & 3,265 & 3,298,634 \\ \hline
    Boston-Cambridge-Newton, MA-NH & 3,120 & 4,941,632 \\ \hline
    Denver-Aurora-Lakewood, CO & 2,785 & 2,963,821 \\ \hline
    Chicago-Naperville-Elgin, IL-IN-WI & 2,673 & 9,618,502 \\ \hline
    Sacramento-Roseville-Folsom, CA & 2,668 & 2,397,382 \\ \hline
    Philadelphia-Camden-Wilmington, PA-NJ-DE-MD & 2,541 & 6,245,051 \\ \hline
    Columbus, OH & 2,533 & 2,138,926 \\ \hline
    Portland-Vancouver-Hillsboro, OR-WA & 2,526 & 2,512,859 \\ \hline
    San Francisco-Oakland-Berkeley, CA & 2,476 & 4,749,008 \\ \hline
	\end{tabular}
	\label{table:table-1}
\end{table}

\par The most active MSAs by total number of posts share some common, predictable traits. First, all of the Metropolitan Areas listed have populations above 1,000,000. While expected, some notable MSAs were not included, such as New York-Newark-Jersey City, NJ-NJ-PA and Los Angeles-Long Beach-Anaheim, CA, which have populations of 20,140,470 and 13,200,998, respectfully. One possible explanation for these discrepancies is the fact that there is no uniform, consistent moderation policy among subreddits (REF). For example, some subreddits automatically filter out all posts and manually approve them, or they disallow certain types of posts (REF - nyc n chicago rules).

\begin{table}[h!]
    \centering
    \small
    \caption{Most active Metropolitan Areas per population}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \begin{tabular}{| c | c | c |}
    \hline
    Metropolitan Statistical Area & Number of Posts & Population\\ \hline
    Bellingham, WA & 1,381 & 226,847 \\ \hline
    Bloomington, IN & 799 & 161,039 \\ \hline
    Missoula, MT & 449 & 117,922 \\ \hline
    Bend, OR & 660 & 198,253 \\ \hline
    Burlington-South Burlington, VT & 546 & 171,415 \\ \hline
    Corvallis, OR & 298 & 95,184 \\ \hline
    Eugene-Springfield, OR & 1,183 & 382,971 \\ \hline
    Charlottesville, VA & 638 & 221,524 \\ \hline
    Ithaca, NY & 299 & 105,740 \\ \hline
    Asheville, NC & 1,312 & 469,015 \\ \hline
	\end{tabular}
	\label{table:table-2}
\end{table}

\par The list of most active MSAs when accounting for population also have some common traits. These MSAs are generally politically liberal (REF) and have large college age populations (REF). These areas have large populations of people that fall under Reddit's main demographic (REF) and, as a result, have correspondingly active communities.

\subsection{Crime Discussion}

\par To first understand the relationship between certain socio-economic variables and the rate of crime discussion, we must first look at crime discussion percentages independently. Of the 161,166 posts gathered, 6,792 are determined to discuss crime by matching certain crime-related keywords to post titles and URLs. Table \ref{table:table-3} lists the Metropolitan Areas with the largest percentage of crime discussion from the total number of posts.

\begin{table}[h!]
    \centering
    \small
    \caption{Metropolitan Areas with most crime discussion}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \begin{tabular}{| c | c | c |}
    \hline
    Metropolitan Statistical Area & \% Crime Posts & \# Crime Posts \\ \hline
    Seattle-Tacoma-Bellevue, WA & 18.2 & 344 \\ \hline
    Anniston-Oxford, AL & 15.7 & 8 \\ \hline
    Lewiston-Auburn, ME & 15.4 & 14 \\ \hline
    Bay City, MI & 14.0 & 7 \\ \hline
    Lewiston, ID-WA & 13.0 & 7 \\ \hline
    Pine Bluff, AR & 12.5 & 4 \\ \hline
    Los Angeles-Long Beach-Anaheim, CA & 12.0 & 257 \\ \hline
    Portland-Vancouver-Hillsboro, OR-WA & 11.4 & 287 \\ \hline
    Rocky Mount, NC & 11.3 & 7 \\ \hline
    Decatur, AL & 10.9 & 7 \\ \hline
    New York-Newark-Jersey City, NY-NJ-PA & 10.7 & 196 \\ \hline
    Flint, MI & 9.7 & 10 \\ \hline
    Morristown, TN & 9.3 & 4 \\ \hline
    Sumter, SC & 9.3 & 5 \\ \hline
    Vallejo, CA & 8.8 & 9 \\ \hline
	\end{tabular}
	\label{table:table-3}
\end{table}

\par On a greater scale, Figure (REF) displays the cumulative distribution function of the data. The average crime discussion percentage lays at 3.5\%.

(FIG)

\par Furthermore, Figure (REF) displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits. The darker the shade of green, the more posts discuss crime.

(FIG)

\subsection{Crime Discussion and Population}

\subsection{Crime Discussion and Politics}

\subsection{Crime Discussion and Documented Crime}

@@

% Appendix A - Metro, subreddit, population, hits
% Appendix B - Metro, population, pop class, Pcrime rate
% Appendix C - Metro, percent dem, pol class, pcrime rate
% Appendix D - Metro, normalized cr, normalized pcr
% Appendix E - Keywords
